---
title: "linear model from Web"
author: "Teresa Juan"
date: "summer 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

```{r}
plot(SIMS~ARM,data=data)
```

In the plot date we can see that as SIMS goes up so does ARM.

### scatterplot

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
```{r}
basicNN + geom_point()
```

This plot shows  us as SIMD increases  so does ARM.


### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

There is a positive correlation between SIMS and ARM, with our numeric result number 0.6860073 showing us a positive  number.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
the residual standard error of 1.226 that’s  the standard deviation across the line, the standard Adjusted R-squared is at  0.467

#### Predict at target point

```{r}
tgp=data.frame(ARM=88, GRIP=94)
predict.lm(model.1, tgp, interval = "prediction")
```

out target point is at low -1.726209 and highest 3.138977.

#### scatterplot with model fit
 

```{r}
basicNN + geom_point() + geom_lm()
```


## Model 2 SIM~GRIP

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

### Now add in scatterplot

```{r}
basicNN + geom_point()
```

In the scatterplot  we can see ther’s  a positive  correlation between SIMS and GRIP. 

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

There’s  is a higher  correlation between SIMS and ARM then in SIMS and GRIP, because SIMS and ARM has a number 0.6860073 and SIMS and GRIP has a number 0.6398458 being lower.

### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

